Models of lens candidates from Space Warps CFHTLS

### 2017-03-21 parts/morph.tex
remove endinput
checking claudes issues

The third diagnostic is whether the lens is fairly isolated, or
whether there are other galaxies in the field that probably contribute
significantly to the lensing.  For this, we do not consider stars or
other clearly foregound objects.  Secondary lensing galaxies can be
marked by the volunteer alongside the spaghetti diagrams.  An example
can be seen as the grey dot and circle in the cutout with SW57 at the
top right of Figure~\ref{fig:splinput}.  Objects marked in this way
are modelled as point masses.  Other possible contributors to lensing
are galaxies or groups or that are not in the immediately vicinity of
the lensed images, yet massive enough to have an effect.  These are
contributed for by allowing a constant but adjustable external shear.

>>>>

The third diagnostic is whether the lens is fairly isolated, or
whether there are other galaxies in the field that probably contribute
significantly to the lensing.  For this, we do not consider stars or
other clearly foregound objects.  Secondary lensing galaxies can be
marked by the volunteer alongside the spaghetti diagrams.  An example
can be seen as the grey dot and circle in the cutout with SW57 at the
top right of Figure~\ref{fig:splinput}.  Objects marked in this way
are modelled as point masses.  Other possible contributors to lensing
are galaxies or groups that are not in the immediately vicinity of
the lensed images, yet massive enough to have an effect.  These are
contributed for by allowing a constant but adjustable external shear.
